---
title: "seaice-alaska"
author: "Sunny Hospital"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The script exports the shape geometries of Alaska fisheries management ecosystem regions using akmarineareas2 package.

devtools::install_github("MattCallahan-NOAA/AKmarineareas")
devtools::install_github("MattCallahan-NOAA/akmarineareas2")

Few code blocks show examples from the readme of the package `akmarinearea2`

```{r readme-akmarinearea2}

## plot NMFS areas
library(akmarineareas2)
library(tidyverse)
library(sf)
## plot NMFS areas and AK
ggplot()+
  geom_sf(data=nmfs, color="red", fill=NA)+
  geom_sf(data=ak)+
  theme_void()

## without dateline removed
my_esr<-esr_dd%>%
  st_shift_longitude()

ggplot()+
  geom_sf(data=my_esr, color="red", fill=NA)+
  theme_void()

## remove dateline
my_esr2<-esr_dd%>%
  remove_dateline()%>%
    st_shift_longitude()
#> Spherical geometry (s2) switched off
  
ggplot()+
  geom_sf(data=my_esr2, color="red", fill=NA)+
  theme_void()

## plot ADFG areas in Southeast AK
#set extent
ext<-data.frame(x=c(-140,-127), y=c(53, 58))%>%
  st_as_sf(coords=c("x", "y"), crs=4326)%>%
  st_transform(crs=3338)%>%
  st_bbox()
#plot adfg areas with canada and ak basemaps
ggplot()+
  geom_sf(data=ak)+
  geom_sf(data=canada)+
  geom_sf(data=adfg, color="black", fill=NA)+
  coord_sf(xlim=c(ext[1], ext[3]), ylim=c(ext[2], ext[4]))+
  theme_bw()
```

Few code blocks show examples from the readme of the package `AKmarineareas`

```{r readme-AKmarineareas}

library(AKmarineareas)

## plot NMFS areas
AK_marine_area()%>%
  st_shift_longitude()%>% #centers on the Pacific
  ggplot()+
  geom_sf()+
  geom_sf_label(aes(label=NMFS_REP_AREA))+
  theme_void()

 
##plot ecosystem subregions, projected version
AK_marine_area(area="Ecosystem Subarea", prj="prj")%>%
  ggplot()+
  geom_sf(aes(fill=Ecosystem_Subarea))+
  theme_void()


```

This code is to map only the Southeastern Bering Sea with a specific color (green)

```{r}
# Create is_se_bering variable 
data <- AK_marine_area(area = "Ecosystem Subarea", prj = "prj") %>%
  mutate(is_se_bering = ifelse(Area_Name == "Southeastern Bering Sea", "Southeastern Bering Sea", "Other"))

# Plot southeastern bering see with green and others grey
ggplot(data) +
  geom_sf(aes(fill = is_se_bering)) +
  scale_fill_manual(values = c("Southeastern Bering Sea" = "#b2cf79", "Other" = "#7f7f7f")) +  
  theme_void()
```

This code exports the shape geometry of the ecosystem subarea "Southeastern Bering Sea"
```{r}

# Examine the object
names(AK_marine_area())
names(AK_marine_area(area="Ecosystem Subarea"))
AK_marine_area(area="Ecosystem Subarea")$Ecosystem_Subarea

# Assign the projected data with epsg: 6393
projected.df <- AK_marine_area(area="Ecosystem Subarea", prj="prj")  

# Assign the data with epsg 4325
dd.df <- AK_marine_area(area="Ecosystem Subarea", prj="dd")  

# Assign the southeastern bering sea 
se_bering <- projected.df[projected.df$Area_Name=="Southeastern Bering Sea",]

# Check the data type
class(se_bering$Shape)

# Check the crs
st_crs(se_bering$Shape) 

# Export the shape to shape file
st_write(se_bering$Shape, "se_bering_sf.shp")

 
```

